\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{physics}
\usepackage{tikz}
\usepackage{mathtools}\mathtoolsset{showonlyrefs}

\newcommand{\td}{\texttt{TESDAQ} }

	
\author{Connor Duncan, Aaron Elersich}
\date{\today}
\title{\td Statement of Work and Design Specification}
\begin{document}
\maketitle
\tableofcontents
\section{Project Objectives}
The objective of this project is to provide a self-contained Data Acquisition and Control System for Dark Matter Search using Phonon Detectors.
\td should provide a method for storing and tracking large binary files from acquisition, as well as desired metadata for these files.
It also should provide a method for tracking and altering the state of various acquisition devices using standard web technologies.
Real-time streaming of large volumes of data should be possible via a specified interface.
\section{Requirements}
\begin{enumerate}
	\item Database which tracks run metadata and file location.
	\item Standard, documented file structure for storage of data.
	\item RESTful API for reading run database, downloading either chunks of or individual files.
	\item In-memory store of current device state
	\item Standard, language-agnostic object for representing device.
	\item RESTful API for CRUD current state.
	\item Socket availability for real-time streaming of data.
	\item Authentication methods and user database with multiple levels of access.
\end{enumerate}
\section{Software Design Description}
The project is broken into two largely independent parts, the Database, and the State.
The database will manage archival work and integrations into offline analysis, as well as storage of authentication tokens and permission levels.
The State will manage the storage, access and alteration of ongoing acquisition activities, as well as the streaming of data in real time to multiple clients.

\subsection{Database}
\subsubsection{File Organization}
Store data as \texttt{<Start>-<Finish>.hd5} where \texttt{<Start>}, \texttt{<Finish>} are given by strings representing \texttt{YYMMDDHHmmSS}.
Each HDF5 file represents a unique run.
Each file will contain the following structure, following the Scientific Data Exchange Format.\footnote{doi:10.1107/S160057751401604X}
\begin{center}
\begin{tabular}{l|ll}
	HDF5 Object	&	HDF5 Object Type	&	Description\\
	\hline
	\emph{exchange}	&	Group			&	Contains measured data tables and metadata table.
	\\
	\emph{implements}	& Group			&	Contains list with implemented tables.
	\\
	\vdots	&	Group/Tables	&	Implemented/derived tables.
\end{tabular}
\end{center}
\subsubsection{Metadata Tracking}
\subsubsection{REST API}


\paragraph{\texttt{/database/runs}} Returns JSON-formatted list of run metadata. Can be sorted by fields using standard GET search parameters.

\paragraph{\texttt{/database/runs/uuid}} Returns JSON-formatted list of file information for run \texttt{uuid}, including size, chunk size, implemented tables.
\subsection{State}
\subsubsection{State Access}
\subsubsection{State Control}
\end{document}
